### 2025-03-27 ms/response_letter.qmd

1. **Improved content and clarity:**
We clarified the study’s main objective, added missing methodological details (e.g., wood density classification criteria and interpretation of $\Delta$LOOIC), and expanded the discussion to address potential confounding effects on allometric relationships.

2. **Enhanced presentation and formatting:**
We standardized the reporting of parameters, corrected figure labels, restructured supplementary tables for better readability, and revised the manuscript language to improve clarity and consistency.

We believe these revisions have strengthened the manuscript by clarifying our objectives, improving consistency and readability, and addressing key methodological concerns—thereby better highlighting the significance of our findings.

We have also updated the data availability statement.
The programming code of this study will be deposited at Zenodo (https://zenodo.org) and made available on Github (<https://github.com/duyenecology/tree-allo>).

@@

> 4) Line 366-369 & Table 2: In the sentence "In addition, the estimated exponent aligns closely with MST predictions for crown radius, supporting the selection of the power-law model for angiosperms, where the community-level exponent b is near the expected *2/3* ($b_{ang}$=0.625775 0.6168636,0.6345041, Table 2)" and the parameter estimates in Table 2, the values are not consistently presented. Check whole of the manuscript for a uniform presentation of the values.

We have standardized the presentation of all parameter estimates throughout the manuscript, including Table 2 and Tables S6-8 and corresponding text.

> 5) Table 1: The table does not clearly explain how much of a difference in ΔLOOIC is considered significant between the two models.

We have revised the caption of Table 1 to clarify that a $\Delta$LOOIC greater than 4 suggests a meaningful difference in predictive performance (line 263-265).

@@

> 8) Supplementary Table S6 is very congested and hard to read. Please revise for better understanding.

We have reformatted Supplementary Tables S6, S7, and S8 for improved readability and included detailed captions to aid interpretation.

> 9) A revision of the English is needed as some sentences aren't properly structured, and it's often difficult to grasp what the authors are saying.

We have revised the manuscript for language, grammar, and sentence structure to enhance clarity and improve overall readability.
For example, we revised lines 482–487 in the Discussion section to ensure sentence brevity and clarity.
Additionally, we updated the figure legends and table captions for greater clarity and carefully cross-checked all technical terms to maintain consistency throughout the text.

### 2025-03-27 ms/response_letter.tex

\author{}
\date{}

\begin{document}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, frame hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, breakable, enhanced, interior hidden]}{\end{tcolorbox}}\fi

@@

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{3}
\tightlist
\item
  Line 366-369 \& Table 2: In the sentence ``In addition, the estimated
  exponent aligns closely with MST predictions for crown radius,
  supporting the selection of the power-law model for angiosperms, where
  the community-level exponent b is near the expected \emph{2/3}
  (\(b_{ang}\)=0.625775 0.6168636,0.6345041, Table 2)'' and the
  parameter estimates in Table 2, the values are not consistently
  presented. Check whole of the manuscript for a uniform presentation of
  the values.
\end{enumerate}
\end{quote}

We have standardized the presentation of all parameter estimates
throughout the manuscript, including Table 2 and Tables S6-8 and
corresponding text.

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{4}
\tightlist
\item
  Table 1: The table does not clearly explain how much of a difference
  in ΔLOOIC is considered significant between the two models.
\end{enumerate}
\end{quote}

We have revised the caption of Table 1 to clarify that a \(\Delta\)LOOIC
greater than 4 suggests a meaningful difference in predictive
performance (line 263-265).

@@

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{7}
\tightlist
\item
  Supplementary Table S6 is very congested and hard to read. Please
  revise for better understanding.
\end{enumerate}
\end{quote}

We have reformatted Supplementary Tables S6, S7, and S8 for improved
readability and included detailed captions to aid interpretation.

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{8}
\tightlist
\item
  A revision of the English is needed as some sentences aren't properly
  structured, and it's often difficult to grasp what the authors are
  saying.
\end{enumerate}
\end{quote}

We have revised the manuscript for language, grammar, and sentence
structure to enhance clarity and improve overall readability. For
example, we revised lines 482--487 in the Discussion section to ensure
sentence brevity and clarity. Additionally, we updated the figure
legends and table captions for greater clarity and carefully
cross-checked all technical terms to maintain consistency throughout the
text.

### 2025-03-27 ms/response_letter.qmd

Corresponding author and contact information:
Key Laboratory of Tropical Forest Ecology, Xishuangbanna Tropical Botanical Garden, Chinese Academy of Sciences, Mengla, Yunnan 666303, China\
Email: katabuchi@xtbg.ac.cn; mattocci27@gmail.com

\newpage

# Responses

Please note that line numbers refer to **ms_diff.pdf** that contains editing history.
The word file has slightly different line numbers.

@@

> 1) In Figure 3, the distinction between species with light and dense wood density is presented. However, the criteria used for this classification are not mentioned in the Materials and Methods section. Clarifying this would improve the transparency of your methodology.

Thank you for pointing this out.
We have added a description in the Methods section clarifying the classification criteria (line 197-202).

> 2) Figure 4 appears to have a formatting issue, as the letters 'a' and 'd' are not displayed.

We were unable to see the absence of the letters "a" and "d" in Figure 4 of the generated PDF file.
Nevertheless, we slightly increased the left margin of the panel labels in case clipping was the cause.
We hope this adjustment addresses the concern and would be happy to make further modifications if needed.

@@

> 4) I found the "Consequences for AGB Estimates" section particularly insightful.

Thank you for your positive feedback.

> 5) Pages 132-140 are blank, likely due to a formatting issue with the final table. The table appears to have fixed columns that prevent the complete display of cell information.

We have reduced the number of significant digits in the tables to prevent column overflow and ensure a complete display of cell information, which should resolve the formatting issue.
These tables were submitted as Excel files, but due to a system-related submission setting, they are still included in the PDF.

### 2025-03-27 ms/response_letter.tex

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  12pt,
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother

\usepackage[default]{sourcesanspro}
\usepackage{sourcecodepro}
\usepackage{xcolor}
\usepackage{mdframed}
% Define blockquote colors
\definecolor{blockquote-border}{RGB}{221,221,221}
\definecolor{blockquote-text}{RGB}{119,119,119}
% Define custom blockquote environment
\newmdenv[
  rightline=false,
  bottomline=false,
  topline=false,
  linewidth=3pt,
  linecolor=blockquote-border,
  skipabove=\parskip,
  innerleftmargin=10pt,
  innerrightmargin=0pt,
  frametitlebackgroundcolor=gray!20
]{customblockquote}
\renewenvironment{quote}
  {\begin{customblockquote}\color{blockquote-text}\ignorespaces}
  {\end{customblockquote}}
\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

On behalf of the authors: Thi Duyen Nguyen

Corresponding author and contact information: Key Laboratory of Tropical
Forest Ecology, Xishuangbanna Tropical Botanical Garden, Chinese Academy
of Sciences, Mengla, Yunnan 666303, China\\
Email: katabuchi@xtbg.ac.cn; mattocci27@gmail.com

\newpage

\section{Responses}\label{responses}

Please note that line numbers refer to \textbf{ms\_diff.pdf} that
contains editing history. The word file has slightly different line
numbers.

@@

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  In Figure 3, the distinction between species with light and dense wood
  density is presented. However, the criteria used for this
  classification are not mentioned in the Materials and Methods section.
  Clarifying this would improve the transparency of your methodology.
\end{enumerate}
\end{quote}

Thank you for pointing this out. We have added a description in the
Methods section clarifying the classification criteria (line 197-202).

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{1}
\tightlist
\item
  Figure 4 appears to have a formatting issue, as the letters `a' and
  `d' are not displayed.
\end{enumerate}
\end{quote}

We were unable to see the absence of the letters ``a'' and ``d'' in
Figure 4 of the generated PDF file. Nevertheless, we slightly increased
the left margin of the panel labels in case clipping was the cause. We
hope this adjustment addresses the concern and would be happy to make
further modifications if needed.

### 2025-03-27 sup/sup.qmd
Update sup.qmd and response letter

![
Allometric relationships between tree height and crown radius versus DBH for angiosperms (a, c) and gymnosperms (b, d) based on three different models: power-law (orange), generalized Michaelis-Menten (green), and Weibull (blue).
The density of overlapping points is represented using a colour gradient ranging from black (low density) to yellow (high density).
Point density was calculated using a 2D kernel density estimation on a 300 $\times$ 300 grid, which estimate the concentration of data points in the log-transformed DBH and tree height or crown radius.
All axes are shown on the log scale.
](../figs/h_cr_dbh_log.png){#fig-compare fig-pos="H"}

>>>>

![
Allometric relationships between DBH and tree height or crown radius in angiosperms (a, c) and gymnosperms (b, d), based on three different models: power-law (orange), generalized Michaelis-Menten (green), and Weibull (blue).
A color gradient from black (low density) to yellow (high density) indicates the density of overlapping data points, calculated via 2D kernel density estimation on a 300 $\times$ 300 grid.
All axes are shown on the log scale.
](../figs/h_cr_dbh_log.png){#fig-compare fig-pos="H"}
